The evolution of gene expression in the term placenta of viviparous mammals

### 2015-11-03 manuscript/manuscript.Rnw
include all go results FDR≤ 0.05

<<go.analysis,warning=FALSE,message=FALSE,echo=FALSE,results="asis">>=
placenta.go.results <- rbindlist(list(placenta_go_results_mf[1:10,],
                             placenta_go_results_bp[1:10,]))
placenta.go.results <- placenta.go.results[,Annotated:=NULL]
setnames(placenta.go.results,"classic","p value")
setnames(placenta.go.results,"classic.fdr","FDR")
setnames(placenta.go.results,"GO.ID","GO ID")
setnames(placenta.go.results,"Term","GO Term")
print(xtable(placenta.go.results,
             digits=2,
             display=c("d","s","s","d","f","e","e","s"),
             caption="Top go MF results",
             label="tab:core_placenta_go_terms"),
      include.rownames=FALSE,
      floating=TRUE,
      booktabs=TRUE,
      size="\\tiny"
      )
@

>>>>

<<go.analysis,warning=FALSE,message=FALSE,echo=FALSE,results="asis">>=
placenta.go.results <- rbindlist(list(placenta_go_results_mf[classic.fdr < 0.05,],
                             placenta_go_results_bp[classic.fdr < 0.05,]))
placenta.go.results <- placenta.go.results[,Annotated:=NULL]
setnames(placenta.go.results,"classic","p value")
setnames(placenta.go.results,"classic.fdr","FDR")
setnames(placenta.go.results,"GO.ID","GO ID")
setnames(placenta.go.results,"Term","GO Term")
print(xtable(placenta.go.results,
             digits=2,
             display=c("d","s","s","d","f","e","e","s"),
             caption="Top go MF results",
             label="tab:core_placenta_go_terms"),
      include.rownames=FALSE,
      floating=TRUE,
      booktabs=TRUE,
      size="\\tiny"
      )
@
